\scshape Topics in mechanism design

### 2025-06-24 ch2.tex
Add files via upload

To rewrite the second term in $R_i(Q_i)$,
let $\phi_i(t_i) \coloneqq \int_0^{t_i} Q_i$;
then integrating by parts yields
%
\begin{multline*}
	\E\left( \int_0^{T_i} Q_i \right)
	= \int_0^1 \phi_i f_i
	= \left[ \phi_i F_i \right]_0^1
	- \int_0^1 \phi_i' F_i
	= \phi_i(1)
	- \int_0^1 Q_i F_i
	\\
	= \int_0^1 Q_i (1-F_i) .
\end{multline*}
%
Let $\boldsymbol{I} : [0,1] \to [0,1]$ denote the identity ($\boldsymbol{I}(t) \coloneqq t$ for every $t \in [0,1]$),
and let $V_i \coloneqq \boldsymbol{I} - \frac{1-F_i}{f_i}$;
this is called agent $i$'s \emph{virtual value.}
We have
%
\begin{equation*}
	R_i(Q_i)
	= \int_0^1 \boldsymbol{I} Q_i f_i
	- \int_0^1 \frac{1-F_i}{f_i} Q_i f_i 
	= \E\left[ V_i(T_i) Q_i(T_i) \right] .
\end{equation*}
%
The right-hand side is equal to
%
\begin{equation*}
	\E\Bigl[ V_i(T_i)
	\E\Bigl( q_i(t_i,\boldsymbol{T}_{-i})
	\Bigm| T_i=t_i \Bigr)
	\Bigr]
	= \E\bigl[ V_i(T_i) q_i(T_i,\boldsymbol{T}_{-i}) \bigr] 
\end{equation*}
%
by definition of $Q_i$ and the law of iterated expectations.
(Recall that agents' types $(T_i)_{i=1}^I$ are independent.)
Thus expected revenue reads
%
\begin{align*}
	R(q)
	&= \E\left[ \sum_{i=1}^I V_i(T_i) q_i(\boldsymbol{T}) \right] .
\end{align*}

@@

		\item $(Q_i)_{i=1}^I$ satisfies the Border inequalities,
		and $Q_i(t_i) \leq E_i$ for every $t_i \in \mathcal{T}_i$ and $i$.

>>>>

To rewrite the second term in $R_i(Q_i)$,
let $\phi_i(t_i) \coloneqq \int_0^{t_i} Q_i$;
then integrating by parts yields
%
\begin{multline*}
	\E\left( \int_0^{T_i} Q_i \right)
	= \int_0^1 \phi_i f_i
	= \left[ \phi_i F_i \right]_0^1
	- \int_0^1 \phi_i' F_i
	= \phi_i(1)
	- \int_0^1 Q_i F_i
	\\
	= \int_0^1 Q_i (1-F_i) .
\end{multline*}
%
Let $\boldsymbol{I} : [0,1] \to [0,1]$ denote the identity ($\boldsymbol{I}(t) \coloneqq t$ for every $t \in [0,1]$),
and let $V_i \coloneqq \boldsymbol{I} - \frac{1-F_i}{f_i}$;
this is called agent $i$'s \emph{virtual value.}
We have
%
\begin{equation*}
	R_i(Q_i)
	= \int_0^1 \boldsymbol{I} Q_i f_i
	- \int_0^1 \frac{1-F_i}{f_i} Q_i f_i 
	= \E\left[ V_i(T_i) Q_i(T_i) \right] .
\end{equation*}
%
The right-hand side is equal to
%
\begin{equation*}
	\E\Bigl[ V_i(T_i)
	\E\Bigl( q_i(t_i,\boldsymbol{T}_{-i})
	\Bigm| T_i=t_i \Bigr)
	\Bigr]
	= \E\bigl[ V_i(T_i) q_i(T_i,\boldsymbol{T}_{-i}) \bigr] 
\end{equation*}
%
by definition of $Q_i$ and the law of iterated expectations.
Thus expected revenue reads
%
\begin{align*}
	R(q)
	&= \E\left[ \sum_{i=1}^I V_i(T_i) q_i(\boldsymbol{T}) \right] .
\end{align*}

@@

		\item $(Q_i)_{i=1}^I$ satisfies the Border inequalities,
		and for each $i$, either $Q_i$ is constant or $Q_i(t_i) \leq E_i$ for every $t_i \in \mathcal{T}_i$.

### 2025-06-24 ch3.tex
Add files via upload

\paragraph{The literature.}
\textcite{JacksonSonnenschein2007} showed that the principal's first-best can be approximated by `linking' the allocations across different periods via something like a discounted quota.
(The theorem in this paper is true as stated, but the proof is wrong: see \textcite{BallJacksonKattwinkel2022} for the correction.)
\textcite{BallKattwinkel2023} go further, characterising the full set of allocations that are implementable via quota mechanisms,%
	\footnote{The result: all and only those that could be implemented using monetary transfers! This result refines an earlier characterisation due to \textcite{MatsushimaMiyazakiYagi2010,Ishii2016}, which concerns \emph{virtual} implementability. (There is a mistake in the former paper; see \textcite{BallKattwinkel2023comment} for the correction.)}
and proving a number of robustness results. (I highly recommend this paper.)
\textcite{Frankel2016jet} is a clear-eyed and general formulation of the quotas idea, with good references references to related work.
\textcite{Frankel2016aej} provides a similarly insightful and general treatment of the idea in \Cref{remark:het}.
(None of these papers considers precisely the model above,
and the mechanisms in Jackson--Sonnenschein and Ball--Kattwinkel are not quite discounted-quota mechanisms in the sense of this chapter.)

@@

The agent's entitlement will eventually hit either $0$ or $\infty$.%
	\footnote{In finite time, almost surely; this follows from the Borel--Cantelli lemma.}
We might call the former `termination'
and the latter `tenure'.
The discounted total quantity supplied is evidently not deterministic (by contrast with discounted-quota mechanisms).

@@

In this section, we'll assume that the agent's valuation is IID over time ($u = 1-d = p$),
and that the agent learns her type in real time (she observes the realisation of $T_n$ only at the dawn of period $n$).
We'll also add an extra `enough patience' assumption:
%
\begin{equation*}
	(1-\delta) (c-\mu)
	\leq \delta \left( 1 - \frac{c}{\ell} \right) \left( \mu - \ell \right) .
\end{equation*}

>>>>

\paragraph{The literature.}
\textcite{JacksonSonnenschein2007} showed that the principal's first-best can be approximated by `linking' the allocations across different periods via something like a discounted quota.
(The theorem in this paper is true as stated, but the proof is wrong: see \textcite{BallJacksonKattwinkel2022} for the correction.)
\textcite{BallKattwinkel2023} go further, characterising the full set of allocations that are implementable via quota mechanisms,%
	\footnote{The result: all and only those that could be implemented using monetary transfers! This result refines an earlier characterisation due to \textcite{MatsushimaMiyazakiYagi2010,Ishii2016}, which concerns \emph{virtual} implementability. (There is a mistake in the former paper; see \textcite{BallKattwinkel2023comment} for the correction.)}
and proving a number of robustness results. (I highly recommend this paper.)
\textcite{Frankel2016jet} is a clear-eyed and general formulation of the quotas idea, with good references to related work.
\textcite{Frankel2016aej} provides a similarly insightful and general treatment of the idea in \Cref{remark:het}.
(None of these papers considers precisely the model above,
and the mechanisms in Jackson--Sonnenschein and Ball--Kattwinkel are not quite discounted-quota mechanisms in the sense of this chapter.)

@@

The agent's entitlement may eventually hit either $0$ or $\infty$.
We might call the former `termination'
and the latter `tenure'.
The discounted total quantity supplied is evidently not deterministic (by contrast with discounted-quota mechanisms).

@@

In this section, we'll assume that the agent's valuation is IID over time ($u = 1-d = p$),
and that the agent learns her type in real time (she observes the realisation of $T_n$ only at the dawn of period $n$).
We'll also add an extra `enough patience' assumption:
%
\begin{equation*}
	(1-\delta) (c-\mu)
	\leq \delta \left( 1 - \frac{c}{h} \right) \left( \mu - \ell \right) .
\end{equation*}
